Practical Optional Types for Clojure

### 2015-02-24 formal-model.tex
section on update

\smallsection{\keype{\k{}}}

\smallsection{Combination}

>>>>

\smallsection{\keype{\k{}}}
Consider the then branch of

\begin{minted}{clojure}
(fn [x :- '{:kw (U nil Keyword)}]
  (when (get x :kw)
    ; here
    ))
\end{minted}

Similar to before,
by T-Abs
{\isprop {\HMapp{\mandatorysetsingleton{\makekw{kw}}{\Union{\Nil}{\Keyword}}}{\emptyabsent}} {\x{}}},
the test's object is {\path{\keype{\makekw{kw}}}{\x{}}} by T-App
and by T-If we assume
{\notprop {\falsy{}} {\path{\keype{\makekw{kw}}}{\x{}}}} in the then branch.

T-Update combines these propositions
$$
\inpropenv {\propenv{}} {\isprop {\update {\HMapp{\mandatorysetsingleton{\makekw{kw}}{\Union{\Nil}{\Keyword}}}{\emptyabsent}} {\nottype {\falsy{}}} {\keype{\makekw{kw}}}} {\x{}}}.
$$
matching the \updateliteral{} case which pushes the \updateliteral{} inside the map
$$
{\HMapp{\mandatorysetsingleton{\makekw{kw}}{\update{\Union{\Nil}{\Keyword}}{\nottype {\falsy{}}}{\emptypath{}}}}{\emptyabsent}}
$$
concluding with
$$
\inpropenv {\propenv{}}
{\isprop {\HMapp{\mandatorysetsingleton{\makekw{kw}}{\Keyword}}{\emptyabsent}}   {\x{}}}.
$$
